Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-09 paper/paper.tex
another pass on III.C

In the following, we describe the list of fuzzers we analyzed. We
initially considered generational grammar-based fuzzers and mutational
fuzzers.

Grammar-based fuzzers generate a new file using the grammar of the
language whose inputs should be fuzzed. Intuitively, those fuzzers
implement a traversal of the production rules of the input grammar to
create syntax trees, which are then pretty-printed. Consequently, this
approach produces inputs that are syntatically valid by construction.
We analyzed two grammar-based
fuzzers--Grammarinator~\cite{grammarinator} and
QuickFuzz~\cite{grieco2016quickfuzz}.  Unfortunately none was
effective out of the box. Given the bound limits we defined, we were
unable to find any discrepancy in the inputs those tools generated. To
sum, the tools produced a high percentage of semantically-invalid
inputs such as \Fix{give one or two concrete examples--variable usage
  without definition?} that we needed to discard and the valid inputs
manifested no discrepancies. For example, we produced 10K inputs with
Grammarinator and only \Fix{X} were valid. With QuickFuzz, we were
able to produce \Fix{Y, Y$>$Y?} valid inputs as it contains some
heuristics to avoid generation of semantically-invalid
inputs. Nonetheless, running those inputs in our infrastructure we
were unable to find discrepancies. Inpecting the valid inputs we found
that they produced only very simple inputs. \Mar{are there weights
  associated with production rules besides the depth you can set?}

@@

Mutational fuzzers can be either white-box (coverage-based) or
black-box. Coverage-based fuzzers like American Fuzz Loop
(AFL)~\cite{afl} and libfuzzer~\cite{libfuzzer} run tests inputs
against instrumented versions of the program under testing with the
typical goal of finding univeral errors like crashes and buffer
overflows. The instrumentation adds code to collect coverage and
monitor properties\footnote{ There are options in the clang toolchain
  to build programs with fuzzing
  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
  for property checking~\cite{clang-documentation}.}. The typical
approach to input generation is evolutionary--these fuzzers try to
minimize the distances to still-uncovered branches of the
program. AFL, for instance, takes the instrumented program binary
(say, a JS engine) and one seed input to that program (say, a JS
program) and produces on output fault-revealing inputs. Considering
our context of application, we needed to instrument one runtime engine
for fuzzing; we chose v8 for this. Unfortunately, we found that most
of the inputs produced by AFL violate the JS grammar. Furthermore, the
fuzzing task took days even when considering only one seed and there
is no simple way to guide the exploration. That happens because the
fuzzer aims to explore the entire decision tree induced from the
engine's main function, including the branches associated with the
lexer and the parser. For that reasons, coverage-based fuzzers were
not considered in this study. It is worth mentioning that Google
mitigates that problem by promoting developers to create fuzz targets
for specific program functions\Fix{cite}. Although that approach has
shown very effective, it requires domain knowledge to create the
calling context to invoke the fuzz target.

>>>>

%% In the following, we describe the list of fuzzers we analyzed. We
%% initially considered generational grammar-based fuzzers and mutational
%% fuzzers.

Fuzzers are typically categorized in two main groups--those that build
inputs anew (generational) and those that modify existing inputs
(mutational). We used two black-box mutational
fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
in this study. In the following, we provide rationale for this
selection.

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction.  We analyzed two
grammar-based fuzzers--Grammarinator~\cite{grammarinator} and
QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately none
was effective out of the box. Given the bound limits we defined on the
number of inputs to generate and the depth of exploration in the
syntax tree, we were unable to find discrepancies on the inputs those
tools generated. To sum, the tools produced a high percentage of
semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
  examples--variable usage without definition?}) that we needed to
discard and the valid inputs manifested no discrepancies. For example,
we produced 10K inputs with Grammarinator and only \Fix{X} of those
were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
valid inputs as it contains some heuristics to circumvent violation of
certain type rules such as \Fix{variable used must be
  defined?}. Nonetheless, running those inputs in our infrastructure
we were unable to find discrepancies. Inpecting those inputs, we
realized that they reflected very simple scenarios. \Mar{are there
  weights associated with production rules besides the depth you can
  set?} To sum, we did not consider this kind of fuzzer in this
study\Fix{...}

@@

Mutational fuzzers can be either white-box or
black-box. White-box mutational fuzzers are typically
coverage-based. American Fuzz Loop
(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of
this kind of fuzzers. These fuzzers run tests inputs
against instrumented versions of the program under testing with the
typical goal of finding univeral errors like crashes and buffer
overflows. The instrumentation adds code to collect branch coverage and
monitor specific properties\footnote{There are options in the clang
  toolchain to build programs with fuzzing
  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
  for property checking~\cite{clang-documentation}.}. The typical
approach to input generation is evolutionary--these fuzzers try to
minimize the distances to still-uncovered branches of the
program. AFL, for instance, takes the instrumented program binary
(say, a JS engine) and one seed input to that program (say, a JS
program) and produces on output fault-revealing inputs, if
found. Considering our context of application, we needed to instrument
one runtime engine for fuzzing; we chose v8. Unfortunately, we found
that most of the inputs produced by AFL violate the JS
grammar. Furthermore, the fuzzing task took days, even when considering
only one seed and there is no simple way to guide the
exploration. That happens because the fuzzer aims to explore the
entire decision tree induced from the engine's main function,
including the branches associated with the lexer and the parser. For
those reasons, coverage-based fuzzers were not considered in this
study. It is worth mentioning that Google mitigates that problem by
promoting developers to create fuzz targets for specific program
functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although that approach has shown very effective,
it requires domain knowledge to create the calling context to invoke
the fuzz target.
